Community-Conditioned Language Models

### 2020-10-30 paper/paper.tex
add pca plots

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

@@

- PCA plots: not conclusive:

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.17}

@@

\input{plot_macros}

@@

As a qualitative assesment of the community embeddings, 
we identified several topic categories into which at least three
of the selected communities fall. 
We plotted the two-component PCA projection of the embeddings,
annotated with these topic categories.
We see that there is some evidence of clustering according to
the topic categories we identified,
suggesting that the embedding space learned by the model is meaningful.

\begin{figure*}
\begin{tikzpicture}
  \commpcagroupplot{floats/lstm-3-1_pca.csv}{floats/transformer-3-3_pca.csv}
\end{tikzpicture}
\caption{Community embedding PCA of the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
\label{fig:lstm-pca}
\end{figure*}
